|

### 2024-12-13 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
Incremental update
Working through Fall updates in hopes I get done before the winter

Stocks <- unique(res.lambda.final$Stock)
res.lambda.fin <- data.frame(res.lambda.final)
six.species <- c('morhua','harengus','aeglefinus','virens','solea','platessa')
pop.dam.6 <- pop.dam |> collapse::fsubset(Species %in% six.species)
for.tunes.6 <- for.tunes |> collapse::fsubset(Species %in% six.species)
dub.time.6 <- dub.time.summary |> collapse::fsubset(Species %in% six.species)
res.lambda.fin$decade <- floor(res.lambda.fin$year/10)*10
res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Stock,decade) |> collapse::fmutate(mn.lam = mean(lam.fish,na.rm=T),
                                                                                 med.lam = median(lam.fish,na.rm=T),
                                                                                 sd.lam = sd(lam.fish,na.rm=T))
res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Species,decade) |> collapse::fmutate(lm.spec.mn = mean(mn.lam,na.rm=T))              
res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Stock) |> 
                                                          collapse::fmutate(
                                                          lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
                                                          lam.fish.mn = mean(lam.fish,na.rm=T),
                                                          lam.org.no.fish.mn = mean(lam.org.no.fish,na.rm=T),
                                                          lam.org.fish.mn = mean(lam.org.fish,na.rm=T),
                                                          lam.no.fish.med = median(lam.no.fish,na.rm=T),
                                                          lam.fish.med = median(lam.fish,na.rm=T),
                                                          lam.org.no.fish.med = median(lam.org.no.fish,na.rm=T),
                                                          lam.org.fish.med = median(lam.org.fish,na.rm=T),
                                                          lam.no.fish.sd = sd(lam.no.fish,na.rm=T),
                                                          lam.fish.sd = sd(lam.fish,na.rm=T),
                                                          lam.org.no.fish.sd = sd(lam.org.no.fish,na.rm=T),
                                                          lam.org.fish.sd = sd(lam.org.fish,na.rm=T)
                                                          ) |> data.frame()
# Get the order right for the stock no species for the boxplots to come later
sns.order <- c("Baltic Sea ", "Baltic Sea 22-24", "Baltic Sea 25-32", "Baltic Sea 28", 
               "North Sea ", "North Sea 4", "North Sea 22-24", "North Sea 4-7 20", "North Sea 6a","North Sea 4 20", "North Sea 7d",     
               "Celtic Sea ","Celtic Sea RA", "Celtic Sea 7a", "Celtic Sea 27.6a", 
               "Irish Sea ","Irish Sea 7a", "Irish Sea 7e","Bay of Biscay ", "NE Arctic ", 
               "Faroes 5a", "Faroes 5b",  "Iceland ", "Iceland 5a",
                "NAFO 2-4 Fa-SGSL", "NAFO 2-4 Sp-SGSL", "NAFO 2-4 SGSL", "NAFO 2-4 NGSL", "NAFO 2-4 NFLD",  
                "NAFO 5-6 ", "NAFO 5-6 GB", "NAFO 5-6 GOM", "NAFO 5-6 EGB",
                "Bering Sea & AI ", "Gulf of Alaska ", "Aleutian Islands ")

@@

dub.time.6 <- dub.time.6 |> collapse::roworder(LME) |>
                             collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
pop.dam <- pop.dam |> collapse::roworder(Species,LME) |>
                       collapse::fmutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
pop.dam.6 <- pop.dam.6 |> collapse::roworder(LME,Area.broad) |>
                       collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
pop.dam$Area.long[pop.dam$Area == "AI"] <- "Aleutian Islands"
pop.dam$Area.long <- factor(pop.dam$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
                                                         "Irish Sea","Bay of Biscay","NE Arctic",
                                                         "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
# I'd also like a pop.dam including fishing
pop.dam.fish <- res.cohort.final |> collapse::fgroup_by(cohort,Stock) |> collapse::fsummarise(gen.len.opt = sum(x.mx.zx.opt)/sum(mx.zx.opt),
                                                                                   gen.len.org = sum(x.mx.zx.org)/sum(mx.zx.org),
                                                                                   R0.opt = sum(mx.zx.opt),R0.org = sum(mx.zx.org))
pop.dam.fish <- left_join(pop.dam.fish,meta.sub,by="Stock")
pop.dam.fish$Area.long[pop.dam.fish$Area == "AI"] <- "Aleutian Islands"
pop.dam.fish$Area.long <- factor(pop.dam.fish$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
                                                         "Irish Sea","Bay of Biscay","NE Arctic",
                                                         "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
pop.dam <- data.frame(pop.dam)

@@

res.lambda.fin.long <- res.lambda.fin |> tidyr::pivot_longer(cols = c(lam.no.fish,lam.fish),names_to = 'group',values_to = 'lambda')
res.lambda.fin.long$Stock.no.species <- factor(res.lambda.fin.long$Stock.no.species,levels = sns.order,ordered = T)
res.lambda.fin.long$group <- substr(res.lambda.fin.long$group,5,20)
res.lambda.fin.long$group <- gsub("\\."," ",res.lambda.fin.long$group)
res.lambda.fin.long.others <- res.lambda.fin.long |> collapse::fsubset(!Species %in% six.species)
res.lambda.fin.long.others$G.Species <- gsub("\\.","",res.lambda.fin.long.others$G.Species)
res.lambda.fin.long.others$G.Species.short <- substr(res.lambda.fin.long.others$G.Species,1,5)
res.lambda.fin.long.6 <- res.lambda.fin.long |> collapse::fsubset(Species %in% six.species)
res.lambda.fin.long.6$G.Species <- gsub("\\.","",res.lambda.fin.long.6$G.Species)

@@

# A table for the estimates at 'interesting' values
comp.lam.res <- do.call('rbind',comp.lam)
# I want to turn this into a table....
comp.lam.res.tab <- comp.lam.res
# Round the numbers
comp.lam.res.tab$min.abund <- round(comp.lam.res.tab$min.abund,digits=2)
rounders <- c("lam.fish.min","lam.fish.40","lam.fish.max",
              "lam.nf.min","lam.nf.40","lam.nf.max")
comp.lam.res.tab[,rounders]      <- round(comp.lam.res.tab[,rounders] ,digits=3)
# Now give it pretty names
tab.names <- c("Minimum Abundance",
               "$\\lambda_{FM>0}^{Min}$",
               "$\\lambda_{FM>0}^{40}$",
               "$\\lambda_{FM>0}^{Max}$",
               "$\\lambda_{FM=0}^{Min}$",
               "$\\lambda_{FM=0}^{40}$",
               "$\\lambda_{FM=0}^{Max}$",
               "Stock","Species")
names(comp.lam.res.tab) <- tab.names

# Now do the same with the differences
comp.lam.diff.res <- do.call('rbind',comp.lam.diff)
# I want to turn this into a table....
comp.lam.diff.res.tab <- comp.lam.diff.res
# Round the numbers
comp.lam.diff.res.tab$min.abund <- round(comp.lam.diff.res.tab$min.abund,digits=2)
rounders <- c("lam.fish.min.40","lam.fish.min.max","lam.fish.40.max",
                    "lam.nf.min.40","lam.nf.min.max","lam.nf.40.max")
comp.lam.diff.res.tab[,rounders] <- round(comp.lam.diff.res.tab[,rounders] ,digits=3)
# Now give it pretty names
tab.names <- c("Minimum Abundance",
               "$\\lambda_{FM>0}^{Min-40}$",
               "$\\lambda_{FM>0}^{Min-Max}$",
               "$\\lambda_{FM>0}^{40-Max}$",
               "$\\lambda_{FM=0}^{Min-40}$",
               "$\\lambda_{FM=0}^{Min-Max}$",
               "$\\lambda_{FM=0}^{40-Max}$",
               "Stock","Species")
names(comp.lam.diff.res.tab) <- tab.names

@@

# Compare the population recovery with the variance, using 2010 because all stocks have a value at 2010... 
# I'm using the overall lambda sd, so the year doesn't actually matter other than to make sure all stocks are included here
# This is used for the recovery variance figure, is this data good?
# How many of the stocks had doubled by year 20, with 75% being my standard, which is a high standard
dub.p.high <- 0.75
dub.p.low <- 0.5
n.dub.10 <- dub.time.summary |> collapse::fsubset(year==10 & prop >= dub.p.high) |> nrow()
n.dub.20 <- dub.time.summary |> collapse::fsubset(year==20 & prop >= dub.p.high) |> nrow()
# Slow stocks, here we define having a low recovery potential has having < 50% of the simulatoins experience a doubling in size.
slow.20 <- dub.time.summary |> collapse::fsubset(year==20 & prop < dub.p.low) 
prop.rec.20 <- dub.time.summary |> collapse::fsubset(year==20) # the proportion that recovers by year 20
lambda.sds <- res.lambda.fin |> collapse::fsubset(year == 2010)
lam.sd.p.rec <- left_join(prop.rec.20,lambda.sds,by=names(prop.rec.20)[c(1,4:24)]) 
lam.sd.p.rec$prop.cat <- "Moderate"
lam.sd.p.rec$prop.cat[lam.sd.p.rec$prop < dub.p.low] <- "Low"
lam.sd.p.rec$prop.cat[lam.sd.p.rec$prop >= dub.p.high] <- "High"
lam.sd.p.rec$prop.cat <- factor(lam.sd.p.rec$prop.cat,levels=c("Low","Moderate","High"))

@@

# the lambda calcs
n.stock.dfo <- meta.sub |> collapse::fsubset(Manage.short == "DFO-TRAC") |> nrow()
n.stock.ices <- meta.sub |> collapse::fsubset(Manage.short == "ICES") |> nrow()
n.stock.noaa <- meta.sub |> collapse::fsubset(Manage.short %in% c("AFSC","NEFSC")) |> nrow()
n.age.0 <- meta.sub |> collapse::fsubset(age.min == 0) |> nrow()
n.age.1 <- meta.sub |> collapse::fsubset(age.min == 1) |> nrow()
n.age.2.plus <- meta.sub |> collapse::fsubset(age.min >= 2) |> nrow()
min.year <- min(res.lambda.fin$year)
max.year <- max(res.lambda.fin$year)
stock.ts.len <- res.lambda.fin |> collapse::fgroup_by(Stock.short) |> collapse::fsummarise(n.years = length(year))
mn.ts.len <- round(mean(stock.ts.len$n.years),digits=1)
min.ts.len <- min(stock.ts.len$n.years)
max.ts.len <- max(stock.ts.len$n.years)
num.orders <- length(unique(meta.sub$Order))
num.gads <- meta.sub |> collapse::fsubset(Order == "Gadiformes") |> nrow()
num.pleur <- meta.sub |> collapse::fsubset(Order == "Pleuronectiformes") |> nrow()
num.scorp <- meta.sub |> collapse::fsubset(Order == "Scorpaeniformes ") |> nrow()
num.clup <- meta.sub |> collapse::fsubset(Order == "Clupeiformes") |> nrow()
num.scomb <- meta.sub |> collapse::fsubset(Order == "Scombriformes") |> nrow()
num.perci <- meta.sub |> collapse::fsubset(Order == "Perciformes") |> nrow()

@@

med.lambda.F0 <- round(median(res.lambda.fin$lam.no.fish),digits=3)
med.r.F0 <- round(median(log(res.lambda.fin$lam.no.fish)),digits=3)*100
med.lambda.F <- round(median(res.lambda.fin$lam.fish),digits=3)
med.r.F <- round(median(log(res.lambda.fin$lam.fish)),digits=3)*100 # median in insensitive to doing median(log(lambda)) or log(median(lamdba)), which makes sense... it's the same point...
mn.lambda.F <- round(mean(res.lambda.fin$lam.fish),digits=2)
# What proportion of the years was lambda < 1 when accounting for fishing
prop.lam.fish.lt.1 <- 100*round(length(which(res.lambda.fin$lam.fish < 1))/nrow(res.lambda.fin),digits=2)
# So if I take the log of the mean of the lambda's I get 0.02, if I take the mean of log(lambda) I get -0.02.  So that's solidly equivocal, but obviously with fishing it is shockingly close to 0 overall
# but also this does make sense really, if it was way less than 0 then everything collapses...
mn.r.F <- round(log(mean(res.lambda.fin$lam.fish)),digits=2) 
# Curious the number of stock in which the mean with fishing is > 1 overall
lambda.by.stock <- res.lambda.fin |> collapse::fgroup_by(Stock.short) |> collapse::fsummarise(mn.lam.nf = mean(lam.no.fish,na.rm=T),
                                                                                              mn.lam.fish = mean(lam.fish,na.rm=T),
                                                                                              med.lam.nf = median(lam.no.fish,na.rm=T),
                                                                                              med.lam.fish = median(lam.fish,na.rm=T))

num.mn.lambda.fish.lt.1 <- length(which(lambda.by.stock$mn.lam.fish < 1))

@@

# Where are the slow ones from
n.not.dub.20 <- nrow(slow.20)
n.alaska <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short== "AFSC"]))
n.nwa <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short %in% c("DFO-TRAC","NEFSC")]))
n.nea <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short %in% c("ICES")]))
n.nafo.24 <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Area.broad %in% "NAFO 2-4"]))
# Now the don't recover ones...
n.alaska.slow <- length(slow.20$Stock.short[slow.20$Manage.short== "AFSC"])
n.nwa.slow <- length(slow.20$Stock.short[slow.20$Manage.short %in% c("DFO-TRAC","NEFSC")])
n.nea.slow <- length(slow.20$Stock.short[slow.20$Manage.short %in% "ICES"])

@@

# New lambda plot with the fishing and no fishing beside each other
# This is likely Figure 1
mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
                4, 10, byrow = TRUE)
new.lam.plt.6 <- ggplot(res.lambda.fin.long.6) + geom_boxplot(aes(y=lambda,interaction(group,Stock.no.species),color=group)) +
                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
                                           scale_x_discrete(NULL, guide = "axis_nested") +
                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
                                           geom_hline(yintercept = 1,linetype='dashed') +
                                           facet_manual(vars(G.Species),design=mat,scales='free_x')+
                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))

save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_6_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 19,base_height = 15)

# The other stocks, perhaps we put this in a supplement...
mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
                7, 7, rep(8,9),
                9, 9, rep(10,7),11,11),
                3, 11, byrow = TRUE)

>>>>

Stocks <- unique(res.lambda.final$Stock)
res.lambda.fin <- data.frame(res.lambda.final)
six.species <- c('morhua','harengus','aeglefinus','virens','solea','platessa')
pop.dam <- pop.dam |> collapse::fgroup_by(Stock) |> 
                           collapse::fmutate(med.gen.len = median(gen.len.opt,na.rm=T),med.r0 = median(R0.opt,na.rm=T)) |>
                           as.data.frame()
pop.dam.6 <- pop.dam |> collapse::fsubset(Species %in% six.species)
for.tunes.6 <- for.tunes |> collapse::fsubset(Species %in% six.species)
dub.time.6 <- dub.time.summary |> collapse::fsubset(Species %in% six.species)
res.lambda.fin$decade <- floor(res.lambda.fin$year/10)*10
res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Stock,decade) |> collapse::fmutate(mn.lam = mean(lam.fish,na.rm=T),
                                                                                 med.lam = median(lam.fish,na.rm=T),
                                                                                 sd.lam = sd(lam.fish,na.rm=T))
res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Species,decade) |> collapse::fmutate(lm.spec.mn = mean(mn.lam,na.rm=T))              
res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Stock) |> 
                                                          collapse::fmutate(
                                                          lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
                                                          lam.fish.mn = mean(lam.fish,na.rm=T),
                                                          lam.org.no.fish.mn = mean(lam.org.no.fish,na.rm=T),
                                                          lam.org.fish.mn = mean(lam.org.fish,na.rm=T),
                                                          lam.no.fish.med = median(lam.no.fish,na.rm=T),
                                                          lam.fish.med = median(lam.fish,na.rm=T),
                                                          lam.org.no.fish.med = median(lam.org.no.fish,na.rm=T),
                                                          lam.org.fish.med = median(lam.org.fish,na.rm=T),
                                                          lam.no.fish.sd = sd(lam.no.fish,na.rm=T),
                                                          lam.fish.sd = sd(lam.fish,na.rm=T),
                                                          lam.org.no.fish.sd = sd(lam.org.no.fish,na.rm=T),
                                                          lam.org.fish.sd = sd(lam.org.fish,na.rm=T)
                                                          ) |> data.frame()
# Get the order right for the stock no species for the boxplots to come later
sns.order <- c("Baltic Sea ", "Baltic Sea 22-24", "Baltic Sea 25-32", "Baltic Sea 28", 
               "North Sea ", "North Sea 4", "North Sea 22-24", "North Sea 4-7 20", "North Sea 6a","North Sea 4 20", "North Sea 7d",     
               "Celtic Sea ","Celtic Sea RA", "Celtic Sea 7a", "Celtic Sea 27.6a", 
               "Irish Sea ","Irish Sea 7a", "Irish Sea 7e","Bay of Biscay ", "NE Arctic ", 
               "Faroes 5a", "Faroes 5b",  "Iceland ", "Iceland 5a",
                "NAFO 2-4 Fa-SGSL", "NAFO 2-4 Sp-SGSL", "NAFO 2-4 SGSL", "NAFO 2-4 NGSL", "NAFO 2-4 NFLD",  
                "NAFO 5-6 ", "NAFO 5-6 GB", "NAFO 5-6 GOM", "NAFO 5-6 EGB",
                "Bering Sea & AI ", "Gulf of Alaska ", "Aleutian Islands ")

@@

dub.time.6 <- dub.time.6 |> collapse::roworder(LME) |>
                             collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
pop.dam <- pop.dam |> collapse::roworder(Species,LME) |>
                       collapse::fmutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
pop.dam.6 <- pop.dam.6 |> collapse::roworder(LME,Area.broad) |>
                       collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
pop.dam$Area.long[pop.dam$Area == "AI"] <- "Aleutian Islands"
pop.dam$Area.long <- factor(pop.dam$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
                                                         "Irish Sea","Bay of Biscay","NE Arctic",
                                                         "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
# I'd also like a pop.dam including fishing
pop.dam.fish <- res.cohort.final |> collapse::fgroup_by(cohort,Stock) |> collapse::fsummarise(gen.len.opt = sum(x.mx.zx.opt)/sum(mx.zx.opt),
                                                                                   gen.len.org = sum(x.mx.zx.org)/sum(mx.zx.org),
                                                                                   R0.opt = sum(mx.zx.opt),R0.org = sum(mx.zx.org))
pop.dam.fish <- left_join(pop.dam.fish,meta.sub,by="Stock")
pop.dam.fish$Area.long[pop.dam.fish$Area == "AI"] <- "Aleutian Islands"
pop.dam.fish$Area.long <- factor(pop.dam.fish$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
                                                         "Irish Sea","Bay of Biscay","NE Arctic",
                                                         "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)

pop.dam.fish <- pop.dam.fish |> collapse::fgroup_by(Stock) |> 
                           collapse::fmutate(med.gen.len = median(gen.len.opt,na.rm=T),med.r0 = median(R0.opt,na.rm=T)) |>
                           as.data.frame()

#pop.dam <- data.frame(pop.dam)

@@

res.lambda.fin.long <- res.lambda.fin |> tidyr::pivot_longer(cols = c(lam.no.fish,lam.fish),names_to = 'group',values_to = 'lambda')
res.lambda.fin.long$Stock.no.species <- factor(res.lambda.fin.long$Stock.no.species,levels = sns.order,ordered = T)
res.lambda.fin.long$group <- substr(res.lambda.fin.long$group,5,20)
res.lambda.fin.long$group <- gsub("\\."," ",res.lambda.fin.long$group)
res.lambda.fin.long <- res.lambda.fin.long |> collapse::fgroup_by(group,Stock) |> collapse::fmutate(med.lam.stock = median(lambda,na.rm=T))

res.lambda.fin.long.others <- res.lambda.fin.long |> as.data.frame() |> collapse::fsubset(!Species %in% six.species)
res.lambda.fin.long.others$G.Species <- gsub("\\.","",res.lambda.fin.long.others$G.Species)
res.lambda.fin.long.others$G.Species.short <- substr(res.lambda.fin.long.others$G.Species,1,5)

res.lambda.fin.long.6 <- res.lambda.fin.long |> as.data.frame() |> collapse::fsubset(Species %in% six.species)
res.lambda.fin.long.6$G.Species <- gsub("\\.","",res.lambda.fin.long.6$G.Species)

@@

# A table for the estimates at 'interesting' values
comp.lam.res <- do.call('rbind',comp.lam)
# I want to turn this into a table....
comp.lam.res.tab <- comp.lam.res
# Round the numbers
comp.lam.res.tab$min.abund <- round(comp.lam.res.tab$min.abund,digits=2)
rounders <- c("lam.fish.min","lam.fish.40","lam.fish.max",
              "lam.nf.min","lam.nf.40","lam.nf.max")
comp.lam.res.tab[,rounders]      <- round(comp.lam.res.tab[,rounders] ,digits=3)
# Now give it pretty names
tab.names <- c("Minimum Abundance",
               "$\\lambda_{F>0}^{Min}$",
               "$\\lambda_{F>0}^{40}$",
               "$\\lambda_{F>0}^{Max}$",
               "$\\lambda_{F=0}^{Min}$",
               "$\\lambda_{F=0}^{40}$",
               "$\\lambda_{F=0}^{Max}$",
               "Stock","Species")
names(comp.lam.res.tab) <- tab.names

# Now do the same with the differences
comp.lam.diff.res <- do.call('rbind',comp.lam.diff)
# I want to turn this into a table....
comp.lam.diff.res.tab <- comp.lam.diff.res
# Round the numbers
comp.lam.diff.res.tab$min.abund <- round(comp.lam.diff.res.tab$min.abund,digits=2)
rounders <- c("lam.fish.min.40","lam.fish.min.max","lam.fish.40.max",
                    "lam.nf.min.40","lam.nf.min.max","lam.nf.40.max")
comp.lam.diff.res.tab[,rounders] <- round(comp.lam.diff.res.tab[,rounders] ,digits=3)
# Now give it pretty names
tab.names <- c("Minimum Abundance",
               "$\\lambda_{F>0}^{Min-40}$",
               "$\\lambda_{F>0}^{Min-Max}$",
               "$\\lambda_{F>0}^{40-Max}$",
               "$\\lambda_{F=0}^{Min-40}$",
               "$\\lambda_{F=0}^{Min-Max}$",
               "$\\lambda_{F=0}^{40-Max}$",
               "Stock","Species")
names(comp.lam.diff.res.tab) <- tab.names

@@

# Compare the population recovery with the variance, using 2010 because all stocks have a value at 2010... 
# I'm using the overall lambda sd, so the year doesn't actually matter other than to make sure all stocks are included here
# This is used for the recovery variance figure, is this data good?
# How many of the stocks had doubled by year 20, with 75% being my standard, which is a high standard
dub.p.high <- 0.75
dub.p.low <- 0.5
n.dub.10 <- dub.time.summary |> collapse::fsubset(year==10 & prop >= dub.p.high) |> nrow()
n.dub.20 <- dub.time.summary |> collapse::fsubset(year==20 & prop >= dub.p.high) |> nrow()
# Slow stocks, here we define having a low recovery potential has having < 50% of the simulatoins experience a doubling in size.
slow.20 <- dub.time.summary |> collapse::fsubset(year==20 & prop < dub.p.low) 
prop.rec.20 <- dub.time.summary |> collapse::fsubset(year==20) # the proportion that recovers by year 20
lambda.sds <- res.lambda.fin |> collapse::fsubset(year == 2010)
lam.sd.p.rec <- left_join(prop.rec.20,lambda.sds,by=names(prop.rec.20)[c(1,4:24)]) 
lam.sd.p.rec$prop.cat <- "Moderate"
lam.sd.p.rec$prop.cat[lam.sd.p.rec$prop < dub.p.low] <- "Low"
lam.sd.p.rec$prop.cat[lam.sd.p.rec$prop >= dub.p.high] <- "High"
lam.sd.p.rec$prop.cat <- factor(lam.sd.p.rec$prop.cat,levels=c("Low","Moderate","High"))
```

@@

# the lambda calcs
n.stock.dfo <- meta.sub |> collapse::fsubset(Manage.short == "DFO-TRAC") |> nrow()
n.stock.ices <- meta.sub |> collapse::fsubset(Manage.short == "ICES") |> nrow()
n.stock.noaa <- meta.sub |> collapse::fsubset(Manage.short %in% c("AFSC","NEFSC")) |> nrow()
n.age.0 <- meta.sub |> collapse::fsubset(age.min == 0) |> nrow()
n.age.1 <- meta.sub |> collapse::fsubset(age.min == 1) |> nrow()
n.age.2 <- meta.sub |> collapse::fsubset(age.min == 2) |> nrow()
n.age.2.plus <- meta.sub |> collapse::fsubset(age.min >= 2) |> nrow()
n.age.3.plus <- meta.sub |> collapse::fsubset(age.min > 2) |> nrow()
min.year <- min(res.lambda.fin$year)
max.year <- max(res.lambda.fin$year)
stock.ts.len <- res.lambda.fin |> collapse::fgroup_by(Stock.short) |> collapse::fsummarise(n.years = length(year))
mn.ts.len <- round(mean(stock.ts.len$n.years),digits=1)
min.ts.len <- min(stock.ts.len$n.years)
max.ts.len <- max(stock.ts.len$n.years)
num.orders <- length(unique(meta.sub$Order))
num.gads <- meta.sub |> collapse::fsubset(Order == "Gadiformes") |> nrow()
num.pleur <- meta.sub |> collapse::fsubset(Order == "Pleuronectiformes") |> nrow()
num.scorp <- meta.sub |> collapse::fsubset(Order == "Scorpaeniformes ") |> nrow()
num.clup <- meta.sub |> collapse::fsubset(Order == "Clupeiformes") |> nrow()
num.scomb <- meta.sub |> collapse::fsubset(Order == "Scombriformes") |> nrow()
num.perci <- meta.sub |> collapse::fsubset(Order == "Perciformes") |> nrow()

@@

med.lambda.F0 <- round(median(res.lambda.fin$lam.no.fish),digits=3)
med.r.F0 <- round(median(log(res.lambda.fin$lam.no.fish)),digits=3)*100
med.lambda.F <- round(median(res.lambda.fin$lam.fish),digits=3)
med.r.F <- round(median(log(res.lambda.fin$lam.fish)),digits=3)*100 # median in insensitive to doing median(log(lambda)) or log(median(lamdba)), which makes sense... it's the same point...
mn.lambda.F <- round(mean(res.lambda.fin$lam.fish),digits=2)
# What proportion of the years was lambda < 1 when accounting for fishing
prop.lam.fish.lt.1 <- 100*round(length(which(res.lambda.fin$lam.fish < 1))/nrow(res.lambda.fin),digits=2)
# So if I take the log of the mean of the lambda's I get 0.02, if I take the mean of log(lambda) I get -0.02.  So that's solidly equivocal, but obviously with fishing it is shockingly close to 0 overall
# but also this does make sense really, if it was way less than 0 then everything collapses...
mn.r.F <- round(log(mean(res.lambda.fin$lam.fish)),digits=2) 
# Curious the number of stock in which the mean with fishing is > 1 overall
lambda.by.stock <- res.lambda.fin |> collapse::fgroup_by(Stock.short) |> collapse::fsummarise(mn.lam.nf = mean(lam.no.fish,na.rm=T),
                                                                                              mn.lam.fish = mean(lam.fish,na.rm=T),
                                                                                              med.lam.nf = median(lam.no.fish,na.rm=T),
                                                                                              med.lam.fish = median(lam.fish,na.rm=T),
                                                                                              years.lt.1.nf = length(which(lam.no.fish<1)),
                                                                                              years.lt.1.fish = length(which(lam.fish<1)),
                                                                                              n.years = length(lam.fish))

# Figure out what proportion of the time stocks have a lambda < 1 and what stocks usually have a lambda less than one
prop.lam.lt.1.nf <-   round(100*median(lambda.by.stock$years.lt.1.nf/lambda.by.stock$n.years),digits = 1)    
prop.lam.lt.1.fish <-   round(100*median(lambda.by.stock$years.lt.1.fish/lambda.by.stock$n.years),digits = 1)
prop.usually.lt.1.nf <- round(100*length(which(lambda.by.stock$years.lt.1.nf/lambda.by.stock$n.years >= 0.5)) /n.stocks,digits=1)                        
prop.usually.lt.1.fish <- round(100*length(which(lambda.by.stock$years.lt.1.fish/lambda.by.stock$n.years >= 0.5)) /n.stocks,digits=1)

max.median.stock <- lambda.by.stock[lambda.by.stock$med.lam.nf == max(lambda.by.stock$med.lam.nf,na.rm=T),]
max.median.lam.nf <- round(max.median.stock$med.lam.nf,digits=2)
min.median.stock <- lambda.by.stock[lambda.by.stock$med.lam.nf == min(lambda.by.stock$med.lam.nf,na.rm=T),]
min.median.lam.nf <- round(min.median.stock$med.lam.nf,digits=2)                                          
mean.nf.of.min.median.lam.nf <- round(min.median.stock$mn.lam.nf,digits=2)
mean.fish.of.min.median.lam.nf <- round(min.median.stock$mn.lam.fish,digits=2)
num.mn.lambda.fish.lt.1 <- length(which(lambda.by.stock$mn.lam.fish < 1))

@@

# Where are the slow ones from
n.not.dub.20 <- nrow(slow.20)
n.alaska <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short== "AFSC"]))
n.nwa <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short %in% c("DFO-TRAC","NEFSC")]))
n.nea <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short %in% c("ICES")]))
n.nafo.24 <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Area.broad %in% "NAFO 2-4"]))
# Now the don't recover ones...
n.alaska.slow <- length(slow.20$Stock.short[slow.20$Manage.short== "AFSC"])
n.nwa.slow <- length(slow.20$Stock.short[slow.20$Manage.short %in% c("DFO-TRAC","NEFSC")]) # All in NAFO 2-4
n.nea.slow <- length(slow.20$Stock.short[slow.20$Manage.short %in% "ICES"])

prop.slow.alaska <- round(100*n.alaska.slow/n.alaska,digits=0)
prop.slow.n24 <- round(100*n.nwa.slow/n.nafo.24,digits=0)

@@

# New lambda plot with the fishing and no fishing beside each other
# This is likely Figure 1

# mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
#                 3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
#                 1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
#                 4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
#                 4, 10, byrow = TRUE)
# new.lam.plt.6 <- ggplot(res.lambda.fin.long.6) + geom_boxplot(aes(y=lambda,interaction(group,Stock.no.species),color=group)) +
#                                            #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
#                                            scale_x_discrete(NULL, guide = "axis_nested") +
#                                            xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
#                                            geom_hline(yintercept = 1,linetype='dashed') +
#                                            facet_manual(vars(G.Species),design=mat,scales='free_x')+
#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))

## New Figure...

mat <- matrix(c(rep(2,14),
                rep(3,8), rep(NA,1), rep(5,5),
                rep(NA,2),rep(4,4),rep(NA,1),rep(6,5),rep(NA,2),
                rep(NA,2),rep(1,9),rep(NA,3)),
                nrow=14, ncol=4,byrow=F)

new.lam.plt.6 <- ggplot(res.lambda.fin.long.6) + geom_boxplot(aes(x=lambda,interaction(group,Stock.no.species),fill=group,color=group)) +
                                           geom_point(aes(x=med.lam.stock,interaction(group,Stock.no.species)),color="firebrick2",fill="firebrick2",shape=8) +
                                           scale_y_discrete(NULL, guide = "axis_nested") +
                                           scale_color_manual(values = c("grey","blue")) +
                                           scale_fill_manual(values = c("grey",'blue')) +
                                           xlab("") + scale_x_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
                                           geom_vline(xintercept = 1,linetype='dashed') +
                                           facet_manual(vars(G.Species),design=mat,scales='free_y')+
                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
